THESIS PROJECT PROPOSAL

### 2019-11-08 project_ashish/paper.tex
commit

\begin{figure}
  \centering
   \includegraphics[scale=0.5]{/home/ashish/Desktop/thesis/pg.png}
  \caption{Important production processes of Standard model Higgs boson in proton collisions.}
   \label{figure 2}
\end{figure}

\begin{figure}
  \centering
   \includegraphics[scale=0.5]{/home/ashish/Desktop/thesis/tq.png}
  \caption{Important production processes of the Higgs boson in proton collisions.}
   \label{figure 3}
\end{figure}

\begin{figure}
  \centering
   \includegraphics[scale=0.5]{/home/ashish/Desktop/cd7.png}
  \caption{ATLAS-CMS combined measurements of coupling strength modifiers.}
   \label{figure 4}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[scale=0.5]{/home/ashish/Desktop/thesis/lum6.png}
  \caption{\onehalfspacing Projected performance of the LHC until 2038, which shows the dates
Preliminary for prolonged stops (LS) of the LHC and luminosities. Points
show instant brightness while the line shows brightness accumulated.}
   \label{figure 5}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=\columnwidth]{/home/ashish/Desktop/thesis/cms.png}
  \caption{\onehalfspacing Leading order Feynman diagrams for the associated production of a single top quark and a Higgs boson in the t channel, where the Higgs boson couples either to the top quark (left) or the W boson (right).}
   \label{figure 6}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[scale=0.5]{/home/ashish/Desktop/thesis/cms5.png}
  \caption{\onehalfspacing Standard model Higgs boson production in association with top quark and top anti-quark, top quarks decaying to W boson and bottom quark, W boson decaying to leptons.}
   \label{figure 7}
\end{figure}

Until the 90's the existence of almost all the particles of the SM were confirmed except the top quark and the Higgs boson. 
These had eluded previous experiments due to difficulties in the production or reconstruction of its decays. The top quark was 
discovered in 1995 in the Tevatron collider of the Fermilab laboratory, this proton collider operated with a center of mass 
energy of 1.8 TeV untill 2010. The LHC collider at the CERN laboratory in Geneva, Switzerland, began its operations in 2010 
colliding protons at 7 TeV increasing the colliding energies to 8 and 13 TeV in the subsequent years. The Compact Muon Solenoid (CMS) is based on the Large Hadron Collider (LHC) located at CERN. It is designed to detect particles known as muons very accurately. The CMS detector has the form of a cylindrical onion, with several concentric layers of components. Needed a powerful magnet to bend charged particles as they move away from the point of collision to identify the charge of the particles to bend them in opposite directions and measure your momentum. A silicon tracker, made of about 75 
million electronic sensors individual arranged in concentric layers, identifies the routes taken by these charged particles bent with very high precision. The muons are not detected by electromagnetic or hadron calorimeters, so special sub-detectors are outside to detect them once they have crossed the solenoid. In 2012, the ATLAS and CMS collaborations, with detectors at two points where the protons collide in the LHC, announced the discovery of a new boson with a mass of 125 GeV. So far, all measurements of the properties of this boson are consistent with those of the Higgs boson of the standard model (SM).\\

@@

\begin{figure}
  \centering
   \includegraphics[width=\columnwidth]{/home/ashish/Desktop/thesis/cms7.jpg}
  \caption{Higgs boson signal strength modifier in various production modes and decay channels.}
   \label{figure 10}
\end{figure}

\begin{figure}
  \centering
   \includegraphics[width=\columnwidth]{/home/ashish/Desktop/cd.png}
  \caption{Leading order Feynman Diagrams for various Higgs production modes.}
   \label{figure 12}
\end{figure}

\begin{figure}
  \centering
   \includegraphics[width=\columnwidth]{/home/ashish/Desktop/cd1.png}
  \caption{Standard model Higgs boson production cross section in various production modes.}
   \label{figure 13}
\end{figure}

\begin{figure}
  \centering
   \includegraphics[width=\columnwidth]{/home/ashish/Desktop/cd2.png}
  \caption{Standard model Higgs boson production cross section with center of mass energy and branching ratios for various decay channels.}
   \label{figure 14}
\end{figure}

\begin{figure}
  \centering
   \includegraphics[width=\columnwidth]{/home/ashish/Desktop/cd3.png}
  \caption{Standard model Higgs boson branching ratios in various decay channels.}
   \label{figure 15}
\end{figure}

\begin{figure}
  \centering
   \includegraphics[width=\columnwidth]{/home/ashish/Desktop/cd5.png}
  \caption{Combined measurement of the products $\sigma$.BR for various production and decay channels of Standard model Higgs boson.}
   \label{figure 17}
\end{figure}

\begin{figure}
  \centering
   \includegraphics[width=\columnwidth]{/home/ashish/Desktop/cd6.png}
  \caption{Likelihood contours in the ($\kappa_F$,$\kappa_V$) plane and combined fit for all decay channels.}
   \label{figure 18}
\end{figure}

\begin{figure}
  \centering
   \includegraphics[width=\columnwidth]{/home/ashish/Desktop/cd7.png}
  \caption{ATLAS-CMS combined measurements of coupling modifiers.}
   \label{figure 19}
\end{figure}

\begin{figure}
  \centering
   \includegraphics[width=\columnwidth]{/home/ashish/Desktop/th.png}
  \caption{Feynman diagrams contributing to the partonic process W b $->$ tH.}
   \label{figure 20}
\end{figure}

\begin{figure}
  \centering
   \includegraphics[width=\columnwidth]{/home/ashish/Desktop/th1.png}
  \caption{Partonic cross sections for the process W b $->$ tH as a function of the center of mass
energy.}
   \label{figure 21}
\end{figure}

\begin{figure}
  \centering
   \includegraphics[width=\columnwidth]{/home/ashish/Desktop/th2.png}
  \caption{Lowest order Feynman diagrams for t-channel tH production in the 4F scheme and in the 5F scheme.}
   \label{figure 22}
\end{figure}

\begin{figure}
  \centering
   \includegraphics[width=\columnwidth]{/home/ashish/Desktop/th3.png}
  \caption{Lowest order Feynman diagrams for s-channel tH production.}
   \label{figure 22}
\end{figure}

>>>>

\begin{figure}
  \centering
   \includegraphics[scale=0.5]{/home/ashish/Desktop/cms12.png}
  \caption{Transverse view of the CMS detector showing the silicon tracker, superconducting solenoid, electromagnetic calorimeter, hadron calorimeter and muon chambers.}
   \label{figure 2}
\end{figure}

\begin{figure}
  \centering
   \includegraphics[scale=0.5]{/home/ashish/Desktop/thesis/pg.png}
  \caption{Important production processes of Standard model Higgs boson ggF, VBF, VH, ttH and tH in proton collisions.}
   \label{figure 3}
\end{figure}

\begin{figure}
  \centering
   \includegraphics[scale=0.5]{/home/ashish/Desktop/thesis/tq.png}
  \caption{Higgs production using the top quark (left) and W boson (right).}
   \label{figure 4}
\end{figure}

\begin{figure}
  \centering
   \includegraphics[scale=0.5]{/home/ashish/Desktop/cd7.png}
  \caption{ATLAS-CMS combined measurements of coupling strength modifiers.}
   \label{figure 5}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[scale=0.5]{/home/ashish/Desktop/thesis/lum6.png}
  \caption{\onehalfspacing Projected performance of the LHC until 2038, which shows the dates
Preliminary for prolonged stops (LS) of the LHC and luminosities. Points
show instant brightness while the line shows brightness accumulated.}
   \label{figure 6}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=\columnwidth]{/home/ashish/Desktop/thesis/cms.png}
  \caption{\onehalfspacing Leading order Feynman diagrams for the associated production of a single top quark and a Higgs boson in the t channel, where the Higgs boson couples either to the top quark (left) or the W boson (right).}
   \label{figure 7}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[scale=0.5]{/home/ashish/Desktop/thesis/cms5.png}
  \caption{\onehalfspacing Standard model Higgs boson production in association with top quark and top anti-quark, top quarks decaying to W boson and bottom quark, W boson decaying to leptons.}
   \label{figure 8}
\end{figure}

Until the 90's the existence of almost all the particles of the SM were confirmed except the top quark and the Higgs boson. 
These had eluded previous experiments due to difficulties in the production or reconstruction of its decays. The top quark was 
discovered in 1995 in the Tevatron collider of the Fermilab laboratory, this proton collider operated with a center of mass 
energy of 1.8 TeV untill 2010. The LHC collider at the CERN laboratory in Geneva, Switzerland, began its operations in 2010 
colliding protons at 7 TeV increasing the colliding energies to 8 and 13 TeV in the subsequent years. The Compact Muon Solenoid (CMS) is based on the Large Hadron Collider (LHC) located at CERN. It is designed to detect particles known as muons very accurately. The CMS detector has the form of a cylindrical onion, with several concentric layers of components. Needed a powerful magnet to bend charged particles as they move away from the point of collision to identify the charge of the particles to bend them in opposite directions and measure your momentum. A silicon tracker, made of about 75 
million electronic sensors individual arranged in concentric layers, identifies the routes taken by these charged particles bent with very high precision. The muons are not detected by electromagnetic or hadron calorimeters, so special sub-detectors are outside to detect them once they have crossed the solenoid \cite{Chatrchyan:2008aa}. In 2012, the ATLAS and CMS collaborations, with detectors at two points where the protons collide in the LHC, announced the discovery of a new boson with a mass of 125 GeV. So far, all measurements of the properties of this boson are consistent with those of the Higgs boson of the standard model (SM).\\

@@

\begin{figure}
  \centering
   \includegraphics[width=\columnwidth]{/home/ashish/Desktop/thesis/cms7.jpg}
  \caption{Higgs boson signal strength modifier in various production modes and decay channels.}
   \label{figure 9}
\end{figure}

\begin{figure}
  \centering
   \includegraphics[width=\columnwidth]{/home/ashish/Desktop/cd.png}
  \caption{Leading order Feynman Diagrams for various Higgs production modes.}
   \label{figure 10}
\end{figure}

\begin{figure}
  \centering
   \includegraphics[width=\columnwidth]{/home/ashish/Desktop/cd1.png}
  \caption{Standard model Higgs boson production cross section in various production modes.}
   \label{figure 11}
\end{figure}

\begin{figure}
  \centering
   \includegraphics[width=\columnwidth]{/home/ashish/Desktop/cd2.png}
  \caption{Standard model Higgs boson production cross section with center of mass energy and branching ratios for various decay channels.}
   \label{figure 12}
\end{figure}

\begin{figure}
  \centering
   \includegraphics[scale=0.5]{/home/ashish/Desktop/cd3.png}
  \caption{Standard model Higgs boson branching ratios in various decay channels.}
   \label{figure 13}
\end{figure}

\begin{figure}
  \centering
   \includegraphics[width=\columnwidth]{/home/ashish/Desktop/cd5.png}
  \caption{Combined measurement of the products $\sigma$.BR for various production and decay channels of Standard model Higgs boson.}
   \label{figure 14}
\end{figure}

\begin{figure}
  \centering
   \includegraphics[width=\columnwidth]{/home/ashish/Desktop/cd6.png}
  \caption{Likelihood contours in the ($\kappa_F$,$\kappa_V$) plane and combined fit for all decay channels.}
   \label{figure 15}
\end{figure}

\begin{figure}
  \centering
   \includegraphics[width=\columnwidth]{/home/ashish/Desktop/cd7.png}
  \caption{ATLAS-CMS combined measurements of coupling modifiers.}
   \label{figure 16}
\end{figure}

\begin{figure}
  \centering
   \includegraphics[width=\columnwidth]{/home/ashish/Desktop/th.png}
  \caption{Feynman diagrams contributing to the partonic process W b $->$ tH.}
   \label{figure 17}
\end{figure}

\begin{figure}
  \centering
   \includegraphics[width=\columnwidth]{/home/ashish/Desktop/th1.png}
  \caption{Partonic cross sections for the process W b $->$ tH as a function of the center of mass
energy.}
   \label{figure 18}
\end{figure}

\begin{figure}
  \centering
   \includegraphics[width=\columnwidth]{/home/ashish/Desktop/th2.png}
  \caption{Lowest order Feynman diagrams for t-channel tH production in the 4F scheme and in the 5F scheme.}
   \label{figure 19}
\end{figure}

\begin{figure}
  \centering
   \includegraphics[width=\columnwidth]{/home/ashish/Desktop/th3.png}
  \caption{Lowest order Feynman diagrams for s-channel tH production.}
   \label{figure 20}
\end{figure}
